### 2022-09-08 chapters/optimization/python-dir/python_interperters.tex
update : techempower

\subsection{python and binarry operations }
The second part of this study, is to look at how different Python implementations work while treating different binary operations .

>>>>

\subsection{python and binarry operations }
The second part of this study is to look at how different Python implementations work while treating different binary operations .
